A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-16 4_method.tex
lil: mention example prefered bead count function

\subsubsection{Initial bead count}
In order to apply a beading strategy to the ST we first assign bead counts to the central regions and then decide on how to apply those bead counts outward.
In order to decide on an initial bead count, we require a function mapping a feature diameter to a bead count: $b: \mathbb{R} \to \mathbb{N}$.
(The feature diameter is twice the radius.)
The function $b$ is determined by the beading strategy and is required to increase monotonically with the input feature diameter.

>>>>

\subsubsection{Initial bead count}
In order to apply a beading strategy to the ST we first assign bead counts to the central regions and then decide on how to apply those bead counts outward.
In order to decide on an initial bead count, we require a function mapping a feature diameter to a bead count: $b: \mathbb{R} \to \mathbb{N}$.
(The feature diameter is twice the radius.)
For example we might choose to round to the nearest integer multiple of some preferred width $w_\text{pref}$: $b(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
The function $b$ is determined by the beading strategy and is required to increase monotonically with the input feature diameter.
